Kindly Bent to Free Us

### 2019-07-08 kindly/infer/infer.tex
fixup! State the theorems.

\subsection{Inference algorithm}

@@

\begin{definition}
  Given a set of variable $U$ and $\unif$, $\unif'$ and $\phi$
  substitutions. \\
  Then
  $\unif \leq^{\phi}_{U} \unif'$ iff $(\phi \circ \unif)|_{U} = \unif'|_U$.
\end{definition}

\begin{definition}
  Given a constraints $C$ and two schemes
  $\schm = \forall \Multi\tvar. \qual{D}{\tau}$ and
  $\schm' = \forall \Multi\tvar'. \qual{D'}{\tau'} $.
  Then $\entail{C}{\schm \preceq \schm'}$
  iff $\entail{C}{\subst{\tvar}{\tau''} D}$
  and $\entail{C\Cand D'}{\Cleq{\subst{\tvar}{\tau''}\tau}{\tau'}}$
\end{definition}

\begin{definition}
A flattened environment,
noted $\Eflat\E$, is the environment
where all the binders are replace by normal ones. More formally:
\begin{align*}
  \Eflat\E
  &= \left\{ \bvar{x}{\tau} \mid
    \bvar{x}{\tau}\in\E
    \vee \bvar{\borrow{x}}{\borrowty{k}{\tau}}\in\E
    \vee \svar{x}{\tau}^n\in\E
    \right\} \cup \left\{ \bvar{\tvar}{k} \mid \bvar{\tvar}{k}\in\E \right\}
\end{align*}
\end{definition}

>>>>

\subsubsection{Inference algorithm}

@@

\begin{definition}[More general unifier]
  Given a set of variable $U$ and $\unif$, $\unif'$ and $\phi$
  substitutions. \\
  Then
  $\unif \leq^{\phi}_{U} \unif'$ iff $(\phi \circ \unif)|_{U} = \unif'|_U$.
\end{definition}

\begin{definition}[Instance relation]
  Given a constraints $C$ and two schemes
  $\schm = \forall \Multi\tvar. \qual{D}{\tau}$ and
  $\schm' = \forall \Multi\tvar'. \qual{D'}{\tau'} $.
  Then $\entail{C}{\schm \preceq \schm'}$
  iff $\entail{C}{\subst{\tvar}{\tau''} D}$
  and $\entail{C\Cand D'}{\Cleq{\subst{\tvar}{\tau''}\tau}{\tau'}}$
\end{definition}

\begin{definition}[Flattened Environment]
A flattened environment,
noted $\Eflat\E$, is the environment
where all the binders are replace by normal ones. More formally:
\begin{align*}
  \Eflat\E
  &= \left\{ \bvar{x}{\tau} \mid
    \bvar{x}{\tau}\in\E
    \vee \bvar{\borrow{x}}{\borrowty{k}{\tau}}\in\E
    \vee \svar{x}{\tau}^n\in\E
    \right\} \cup \left\{ \bvar{\tvar}{k} \mid \bvar{\tvar}{k}\in\E \right\}
\end{align*}
\end{definition}
